Simulations to test ctwas summary stats version, 45k samples

### 2021-04-22 analysis/SNP-harmonization.Rmd
add coloc
focus results

* Fusion weights files: They use .bim format for SNP information, so 5th column is Alt, 6th column is Ref.

@@

@@

eQTL information were obtained from FUSION pre-trained models. We used all SNPs with weights != 0 in

>>>>

* Fusion weights files: They use .bim format for SNP information, so 5th column is Alt, 6th column is Ref. Effect size in `wgt.matrix` variable is defined using Alt as effect ellele (5th column in `snps` variable).

@@

* plink association tests: see [here](http://zzz.bwh.harvard.edu/plink/anal.shtml). For the additive effects of SNPs, the direction of the regression coefficient represents the effect of each extra minor allele (i.e. a positive regression coefficient means that the minor allele increases risk/phenotype mean). If the --beta command is added along with --logistic, then the regression coefficients rather than the odds ratios will be returned.
NOTE:Elsewhere in plink, the term reference allele is sometimes used to refer to A1, i.e. the --reference-allele command can be used to specify which allele is A1. Note that in association testing, the odds ratios, etc are typically calculated with A2 as the actual reference allele (i.e. a positive OR means A1 increases risk relative to A2).

* GTEx summary statistics: The normalized effect size (NES) of the eQTLs is defined as the slope of the linear regression, and is computed as the effect of the alternative allele (ALT) relative to the reference allele (REF) in the human genome reference GRCh38/hg38 (i.e., the eQTL effect allele is the ALT allele). See [here](https://www.gtexportal.org/home/documentationPage).

* GEMMA: "chr    rs  ps  n_miss  allel1  allel0  af  beta    se  l_remle p_wald". The 11 columns are: chromosome, SNP ID, basepair position, number of missing values for a given SNP, the effect (coded) allele, the other allele, frequency of the effect allele, effect size, standard error, lambda and p-value ([http://www.xzlab.org/software.html]).

@@

eQTL information were obtained from FUSION pre-trained models. We used all SNPs with weights != 0 in lasso trained models.

### 2021-04-22 analysis/simulation-ctwas-ukbWG-gtex.adipose_s40.22.Rmd
focus results

```{r libs}
library(ctwas)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
library(stringr)
source("~/causalTWAS/causal-TWAS/analysis/summarize_ctwas_plots.R")
source('~/causalTWAS/causal-TWAS/analysis/summarize_twas-coloc_plots.R')
source('~/causalTWAS/causal-TWAS/code/qqplot.R')
```

@@

    f1 <- caliFUSIONp_plot(phenofs, fusioncolocfs)
    f2 <- ncausalFUSIONp_plot(phenofs, fusioncolocfs)
    f3 <- caliPP4_plot(phenofs, fusioncolocfs)
    f4 <- ncausalPP4_plot(phenofs, fusioncolocfs)
    gridExtra::grid.arrange(f1, f2, ncol=2)
    gridExtra::grid.arrange(f3, f4, ncol=2)
}
```

@@

simutags <- paste(1, c(2,4,5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(2, c(2,4), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag2, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(3, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(4, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(5, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(6, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(7, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(8, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(9, 1:4, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(10, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
```

>>>>

```{r libs}
library(ctwas)
library(data.table)
suppressMessages({library(plotly)})
library(tidyr)
library(plyr)
library(stringr)
source("~/causalTWAS/causal-TWAS/analysis/summarize_ctwas_plots.R")
source('~/causalTWAS/causal-TWAS/analysis/summarize_twas-coloc_plots.R')
source('~/causalTWAS/causal-TWAS/analysis/summarize_focus_plots.R')
source('~/causalTWAS/causal-TWAS/code/qqplot.R')
```

@@

    f1 <- caliFUSIONp_plot(phenofs, fusioncolocfs)
    f2 <- ncausalFUSIONp_plot(phenofs, fusioncolocfs)
    f3 <- caliPP4_plot(phenofs, fusioncolocfs, twas.p = 0.05/J)
    f4 <- ncausalPP4_plot(phenofs, fusioncolocfs, twas.p = 0.05/J)
    gridExtra::grid.arrange(f1, f2, ncol=2)
    gridExtra::grid.arrange(f3, f4, ncol=2)
}

plot_focus <- function(configtag, runtag,  simutags){
    phenofs <- paste0(outputdir, runtag, "_simu", simutags, "-pheno.Rd")
    focusfs <- paste0(comparedir, runtag, "_simu", simutags, ".Adipose_Subcutaneous_setalleleUKB.focus.tsv")

    f1 <- califocusPIP_plot(phenofs, focusfs)
    f2 <- ncausalfocusPIP_plot(phenofs, focusfs)
    gridExtra::grid.arrange(f1, f2, ncol=2)
}
```

@@

simutags <- paste(1, c(2,4,5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(2, c(2,4), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag2, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(3, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(4, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(5, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(6, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(7, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(8, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(9, 1:4, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(10, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
```

### 2021-04-22 analysis/simulation-ctwas-ukbWG-gtex.adipose_s40.22_041521.Rmd
focus results

---
title: "Simulations (mix normal prior), ctwas_rss, 22k samples"
output: html_document
---

@@

```{r files}
pgenfn = "/home/simingz/causalTWAS/ukbiobank/ukb_pgen_s40.22/ukb-s40.22_pgenfs.txt"
ld_pgenfn = "/home/simingz/causalTWAS/ukbiobank/ukb_pgen_s40.22/ukb-s40.22.2_pgenfs.txt"
outputdir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20210215/" # /
comparedir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20210215_compare/"
runtag = "ukb-s40.22-adi"
configtags = 1
simutags = paste(rep(1:2, each = length(1:5)), 1:5, sep = "-")

@@

      To simulate phenotype data, first we impute gene expression based on expression models, then we set gene/SNP pi1 and PVE, get rough effect size for causal SNPs and genes and simulate phenotype under the mixture of normal distributions.

* The prior distribution for causal effect: 
```{r }

nmix <- 4
pi_k <- rep(1/nmix, nmix)

ra <- 2**(1: length(pi_k))
sa2_kr <-  ra / (pi_k * sum(ra))

cat("number of mixtures: ", nmix, "\n")
cat("variance of each component:", sa2_kr, "\n")

hist(mixtools::rnormmix(2000, lambda = pi_k,
                        mu = rep(0, length(pi_k)),
                        sigma = sa2_kr), breaks = 100, main = "prior distribution", xlab = "")
```

Then we performed GWAS for all SNPs and get z scores for each by univariate linear regression.

@@

2. Run ctwas_rss
We used LDetect to define regions. `ctwas_rss` algorithm first runs on all regions to get rough estimate for gene and SNP prior. Then run on small regions (having small probablities of having > 1 causal signals based on rough estimates) to get more accurate estimate. To lower computational burden, we downsampled SNPs (0.1), estimate parameters. We run susie for all regions using estimated parameters, select regions with strong gene signals (max gene PIP > 0.8) and rerun using full SNPs for these regions.

@@

# `ctwas` results + other comparators

@@

We run FUSION following default settings and adjust p values by BH method to get expected FDP.
we ran coloc for all genes with TWAS p < 1e-4. We use PP4 (SNP associate with both traits).

@@

plot_PIP <- function(configtag, runtag,  simutags){
   phenofs <- paste0(outputdir, "ukb-s40.22-adi", "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(outputdir, runtag, "_simu",simutags, "_config", configtag,".susieIrss.txt")

@@

```{r param, fig.height=3, fig.width=10, message=F}

@@

simutags <- paste(1, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(2, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

@@

simutags <- paste(9, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

>>>>

---
title: "Simulations to test ctwas summary stats version, 22k samples"
output: html_document
---

@@

```{r files}
pgenfn = "/home/simingz/causalTWAS/ukbiobank/ukb_pgen_s40.22/ukb-s40.22_pgenfs.txt"
ld_pgenfn = "/home/simingz/causalTWAS/ukbiobank/ukb_pgen_s40.22/ukb-s40.22.2_pgenfs.txt"
outputdir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20210415/" # /
comparedir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20210415_compare/"
runtag = "ukb-s40.22-adi"
configtags = 1
simutags = paste(rep(1:2, each = length(1:5)), 1:5, sep = "-")

@@

      To simulate phenotype data, first we impute gene expression based on expression models, then we set gene/SNP pi1 and PVE, get rough effect size for causal SNPs and genes and simulate phenotype under the sparse model with spike and slab prior.
      Then we performed GWAS for all SNPs and get z scores for each by univariate linear regression.

@@

2. Run ctwas_rss
We used LDetect to define regions. `ctwas_rss` algorithm first runs on all regions to get rough estimate for gene and SNP prior. Then run on small regions (having small probablities of having > 1 causal signals based on rough estimates) to get more accurate estimate. To lower computational burden, we downsampled SNPs (0.1), estimate parameters and convert back to orginal scale. Lastly, run susie with given L for all regions and for all genes and SNPs using estimated prior and prior variance.

@@

# `ctwas` results

@@

@@

plot_PIP <- function(configtag, runtag,  simutags){
   phenofs <- paste0(outputdir, runtag, "_simu", simutags, "-pheno.Rd")
   susieIfs <- paste0(outputdir, runtag, "_simu",simutags, "_config", configtag,".susieIrss.txt")

@@

```{r param2, fig.height=3, fig.width=8, message=F}

@@

simutags <- paste(1, c(1:5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(2, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag2, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

@@

simutags <- paste(9, 1:4, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

### 2021-04-22 analysis/simulation-ctwas-ukbWG-gtex.adipose_s40.22_mixnormal.Rmd
focus results

    f1 <- caliFUSIONp_plot(phenofs, fusioncolocfs)
    f2 <- ncausalFUSIONp_plot(phenofs, fusioncolocfs)
    f3 <- caliPP4_plot(phenofs, fusioncolocfs, twas.p = 0.05/J)
    f4 <- ncausalPP4_plot(phenofs, fusioncolocfs, twas.p = 0.05/J)
    gridExtra::grid.arrange(f1, f2, ncol=2)
    gridExtra::grid.arrange(f3, f4, ncol=2)
}
```

@@

simutags <- paste(1, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(2, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(3, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(4, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(5, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(6, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(7, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(8, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(9, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(10, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
```

>>>>

    f1 <- caliFUSIONp_plot(phenofs, fusioncolocfs)
    f2 <- ncausalFUSIONp_plot(phenofs, fusioncolocfs)
    f3 <- caliPP4_plot(phenofs, fusioncolocfs, twas.p = 0.05/J)
    f4 <- ncausalPP4_plot(phenofs, fusioncolocfs, twas.p = 0.05/J)
    gridExtra::grid.arrange(f1, f2, ncol=2)
    gridExtra::grid.arrange(f3, f4, ncol=2)
}

plot_focus <- function(configtag, runtag,  simutags){
    phenofs <- paste0(outputdir, runtag, "_simu", simutags, "-pheno.Rd")
    focusfs <- paste0(comparedir, runtag, "_simu", simutags, ".Adipose_Subcutaneous_setalleleUKB.focus.tsv")

    f1 <- califocusPIP_plot(phenofs, focusfs)
    f2 <- ncausalfocusPIP_plot(phenofs, focusfs)
    gridExtra::grid.arrange(f1, f2, ncol=2)
}
```

@@

simutags <- paste(1, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(2, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(3, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(4, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(5, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(6, 2:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(7, c(1:3,5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(8, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(9, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(10, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
```

### 2021-04-22 analysis/simulation-ctwas-ukbWG-gtex.adipose_s80.45.Rmd
focus results

simutags <- paste(1, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag2, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(2, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(3, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(4, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(5, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(6, 2:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(7, c(1:3,5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(8, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(9, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)

simutags <- paste(10, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
```

>>>>

simutags <- paste(1, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag2, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(2, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(3, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(4, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(5, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(6, 2:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(7, c(1:3,5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(8, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(9, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)

simutags <- paste(10, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
```
